Argennon: A Scalable Smart Contract Platform

### 2022-04-20 tex/sections/avm.tex
Remove outdated parts
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Clarify resource management
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Resource usage can be measured per session or per application call. Obviously per session measurement is
easier and more efficient. However, when we measure resources per session if
a session violates its resource caps, determining the point of failure may require precise and error-free resource
measurement. Note that for implementing optional decoupling principle, we need to determine the exact application call
which has failed in a call chain. For example, assume that a session containing an application call
violates a 2 milliseconds execution time cap. If in the caller's code, the call happens exactly after 2 milliseconds,
a small fluctuation in the execution time measurement can
change the point of failure between the called and the caller application. This can introduce nondeterministic
behaviour which could make block validation impossible. That's why the AscEE sometimes uses per application call
resource management. If we define the resource caps per application call and perform our measurements for each
application call separately, by using caps that are larger than the measurement error, errors in the
measurements would not change the point of failure in the call chain.

The AscEE has two type of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and default pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). An optimistic session must
always complete normally, a monitored session is allowed to either complete normally or abruptly. In Argennon, the
type of execution session for each transaction is decided by the block proposer.

@@

    Each application call has some amount of \texttt{externalClocks}. When an application makes a request to another
    application it has to \emph{forward} a portion of its \textbf{external} clocks to the called application. This
    amount will determine the value of \texttt{maxClocks} for the called application.

@@

In Argennon, execution time and local memory are considered \emph{nondeterministic} resources. A nondeterministic
resource is a resource that can not be measured precisely and its measurement always contains a random error.

>>>>

Resource usage can be measured per session or per application call. Obviously per session measurement is
easier and more efficient. However, when we measure resources per session if
a session violates its resource caps, determining the point of failure may require precise and error-free resource
measurement. Note that for implementing optional decoupling principle in Argennon, we need to determine the exact
application call which has failed in a call chain. For example, assume that a session containing an application call
violates a 2 milliseconds execution time cap. If in the caller's code, the call happens exactly after 2 milliseconds,
a small fluctuation in the execution time measurement can
change the point of failure between the called and the caller application. This can introduce nondeterministic
behaviour which could make block validation impossible. That's why the AscEE sometimes uses per application call
resource management. If we define the resource caps per application call and perform our measurements for each
application call separately, by using caps that are larger than the measurement error, errors in the
measurements would not change the point of failure in the call chain.

The AscEE has two type of execution sessions: \emph{optimistic} and \emph{monitored}. Resource usage of an optimistic
session is always measured per session and default pre-defined resource caps are used. On the other hand, for a
monitored session, resources that can not be measured precisely are measured per application call and their caps are
determined per application call by the external HTTP request (i.e.\ transaction). In Argennon, the
type of execution session for each transaction is decided by the block proposer.

@@

    Each application call has some amount of \texttt{externalClocks}. When an application makes a request to another
    application it has to \emph{forward} a portion of its \textbf{external} clocks to the called application. This
    amount will determine the value of \texttt{maxClocks} for the called application, and is subtracted from the value
    of \texttt{externalClocks} of the caller.

@@

In Argennon, execution time and local memory are considered \emph{nondeterministic} resources. A nondeterministic
resource is a resource that can not be measured precisely and its measurement always contains a random error.
Optimistic sessions are not allowed to fail because of violating nondeterministic resource limits. As a result, the
block proposer must always choose a monitored session for a transaction that violates a nondeterministic resource cap
and is included in his block.
